Figures

### 2019-04-30 figures/07_model-selection.Rmd
summarize posteriors

```{r brms_stan}
library(brms)

names(dt) <- gsub("_", "v", names(dt))
dt        <- dplyr::filter(dt, !is.na(phosphorusvfertilizervuse), 
                    !is.na(soybeans))

# linear
# model_form <- bf(tp ~ agvpct)

@@

# plot(fit1, pars = "bagvpct")

get_variables(fit)
spread_draws(fit, b_Intercept)

test <- spread_draws(fit, r_hu4vzoneid[hu4vzoneid,term]) %>%
  dplyr::filter(term == "agvpct" & hu4vzoneid == "HU4_40")

>>>>

```{r brms_stan}
library(brms)
library(tidybayes)

dt        <- readRDS("../data/dt.rds") %>% 
  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", 
                "ag_pct", "phosphorus_fertilizer_use", "soybeans")
names(dt) <- gsub("_", "v", names(dt))
dt        <- dplyr::filter(dt, !is.na(phosphorusvfertilizervuse), 
                    !is.na(soybeans))

# linear
model_form <- bf(tp ~ agvpct)
fit0 <- brm(formula = model_form, data = dt, 
           family = gaussian())

get_variables(fit0)
plot(fit0, pars = "agvpct")

@@

# pull global distribution (lower, mean, upper)
# get_variables(fit0)
global_dist <- spread_draws(fit0, b_agvpct) %>%
    mutate(hu4vzoneid = "global") %>%
    group_by(hu4vzoneid) %>%
    do(tibble::as_tibble(t(quantile(.$b_agvpct, c(0.05, 0.5, 0.95)))))

# pull hu4 distribution (lower, mean, upper)
hu4_dist <- spread_draws(fit, r_hu4vzoneid[hu4vzoneid,term]) %>%
  dplyr::filter(term == "agvpct") %>%
  group_by(hu4vzoneid) %>%
  do(tibble::as_tibble(t(quantile(.$r_hu4vzoneid, c(0.05, 0.5, 0.95))))) %>%
  mutate(signif = case_when(`5%` > 0 ~ TRUE))

all_dist <- bind_rows(global_dist, hu4_dist)

ggplot(data = all_dist) +
  geom_point(aes(x = hu4vzoneid, y = `50%`)) +
  geom_errorbar(aes(ymin = `5%`, ymax = `95%`, x = hu4vzoneid, color = signif)) +
  geom_hline(yintercept = 0) +
  coord_flip()

hu4_signif <-  LAGOSNEgis::query_gis(
  "HU4", "ZoneID", dplyr::filter(hu4_dist, signif)$hu4vzoneid) %>% 
  st_cast(to = "MULTIPOLYGON")

# pull 2nd level covariate distributions
get_variables(fit2)
# spread_draws(fit, b_Intercept)

plot(fit, pars = "agvpct")

test <- spread_draws(fit, r_hu4vzoneid[hu4vzoneid,term]) %>%
  dplyr::filter(term == "agvpct") %>%
  group_by(hu4vzoneid) %>%
  summarise(agvpct_effect = median(r_hu4vzoneid))
quantile(test$agvpct_effect, c(0.05, 0.5, 0.95))
